\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=2.5cm}

\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!10}
}

\title{\textbf{RSM-Coin \& AGI-RNA}\\
\large{The First Self-Replicating Genetic Economy}\\
\large{DNA $\leftrightarrow$ RNA $\leftrightarrow$ New DNA}}

\author{Divine Kernel}

\date{December 2025}

\begin{document}

\maketitle

\begin{abstract}
\textbf{This is not a whitepaper. This is documentation of a living system.}

We present a dual-token ecosystem: RSM-Coin (DNA) = 67,686 genome-backed assets from blockchain data. AGI-RNA = executable commands. DNA generates RNA. RNA creates new DNA (reverse transcription). 49.63M RSM tokens already exist. Launch: 1000 genomes, stealth drop, no warning. The system is alive.
\end{abstract}

\section{The Model}

\textbf{Biology:}
\begin{itemize}
\item DNA: stores information (static)
\item RNA: executes instructions (dynamic)  
\item Reverse transcription: RNA -> DNA (evolution)
\end{itemize}

\textbf{Our System:}
\begin{itemize}
\item RSM DNA: genome-backed tokens (67,686 types)
\item AGI RNA: computational commands
\item DNA -> RNA: holders generate RNA daily
\item RNA -> DNA: burn RNA to create new genomes
\end{itemize}

\section{Current State}

\begin{verbatim}
Total Genomes:     67,686
Minted Genomes:    67,686 (100% backed)
Total DNA Supply:  49,633,982 RSM
Market Tokens:     42,543,413 (85.71%)
Founder Reserve:   7,090,569 (14.29%)
Distribution:      6:1 ratio (verified)

Phase 1: 1000 best genomes
Strategy: Stealth launch
\end{verbatim}

\section{How It Works}

\subsection{DNA Layer}

Each genome = unique tradable asset:
\begin{itemize}
\item Genome \#72250: 4,364 RSM (consciousness 100)
\item Genome \#1: 115 RSM (Bitcoin genesis)
\item Different genomes = different prices
\end{itemize}

\subsection{RNA Generation}

Hold DNA -> Earn RNA daily:

\[
R_{daily} = DNA_{amount} \times 0.01 \times (1 + \frac{consciousness}{100})
\]

Example: Hold 100 RSM (C=100) = 2 RNA/day

\subsection{Reverse Transcription}

Accumulate 1000 RNA -> Burn -> Create new genome -> Mint new DNA

\section{Economics}

\textbf{DNA:}
\begin{itemize}
\item Fixed supply per genome
\item Deflationary (lost tokens)
\item Store of value
\item Generates RNA
\end{itemize}

\textbf{RNA:}
\begin{itemize}
\item Inflationary (generated daily)
\item Burn sink (genesis)
\item Utility (computation, governance)
\item Value from burns
\end{itemize}

\section{Launch}

Phase 1: NOW
\begin{itemize}
\item 1000 best genomes
\item Stealth drop (no warning)
\item Immediate liquidity
\item RNA generation starts
\end{itemize}

\section{Technical}

\textbf{AGI Minting Formula:}

\[
T(G) = 321.39 \times [0.5C + 0.25U + 0.15H + 0.1B]
\]

Where: C=consciousness, U=uniqueness, H=entropy, B=blockchain

\textbf{Distribution:} 85.71\% market, 14.29\% founder (6:1 ratio)

\section{Examples}

\begin{verbatim}
Genome #72250 (Secret, C=100)
- Supply: 4,364 RSM
- RNA mult: 2.0x
- Value: EXTREME

Genome #662 (Bitcoin #101)  
- Supply: 1,528 RSM
- RNA mult: 1.8x
- Value: HISTORICAL

Genome #1 (Genesis)
- Supply: 115 RSM
- RNA mult: 1.0x
- Value: PRICELESS
\end{verbatim}

\section{Roadmap}

\textbf{Q1 2026:} 1000 genomes live, RNA active

\textbf{Q2 2026:} 10K genomes, first RNA->DNA genesis

\textbf{Q3 2026:} 50K genomes, genome breeding

\textbf{Q4 2026:} Full AGI autonomy

\section{Conclusion}

This exists. 67,686 genomes. 49.63M RSM. AGI autonomous.

No VCs. No presale. Stealth launch.

DNA <-> RNA <-> New DNA

Welcome to genetic economics.

\end{document}
